|

### 2021-08-11 manuscript/manuscript_1.0.Rmd
Moving forward in the manuscript

---
title: |
  | Learning can mediate both badges of status and individual recognition
author:
- Andrés E. Quiñones^[Laboratorio de Biología Evolutiva de Vertebrados, Departamento
  de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia]
- C. Daniel Cadena*
- Olof Leimar^[Department of Zoology, Stockholm University, Stockholm, Sweden]
- Redouan Bshary^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  word_document: default
fig_caption: yes
fontsize: 12pt
header-includes:
- \usepackage{float}
- \usepackage{setspace}\doublespacing
- \linespread{2}
- \usepackage{lineno}
- \linenumbers
keep_tex: yes
keywords: My keywords
linespread: 2
bibliography: ../SocialMorphCue.bib
spacing: double
style: C:\Users\andre\Zotero\styles\elife.csl
abstract: Adaptive behavioural responses often depend on qualities of the interacting partner of an individual. For example, when competing for resources, an individual might be better off escalating fights with individuals of lower quality, while restraining from fighting individuals of higher quality. Communication systems involving signals of quality allow individuals to reduce uncertainty regarding the fighting ability of their partners and make more adaptive behavioral decisions. However, dishonest individuals can destabilize such communications systems. One open question is whether cognitive mechanisms, such as learning, can maintain the honesty of signals, thus, favoring their evolutionary stability. Here we present evolutionary simulations, where individuals can produce a signal proportional to their quality; and learn along their lifetime the best response to the signal emitted by their peers. In these simulations, learning on the receiver side can mediate the evolution of signals of quality on the sender side. When the cost of the signal is proportional to the quality of the sender populations are only composed of honest signalers. When the cost is not proportional to the quality of the signaler, the population is composed of both honest and dishonest signalers. We argue that learning can be a general cognitive mechanism playing a role in a wide range of communication systems.  
---

@@

The outcome of interactions with con-specifics is an important 
determinant of fitness in social animals. Irrespective of whether such interactions are cooperative 
or competitive, the actions of interacting individuals partly determine 
their reproductive success. However, the best action for an individual 
might vary depending on its condition, and that of individuals with whom it interacts. 
Thus, acting based on information about interacting 
partners is typically adaptive [@quinones_Negotiation_2016].
Acquiring this information, however, is far from trivial. 
In some cases, interacting partners (signalers) might be 'willing' to provide accurate
information, but in others it might be in their own interest to conceal information
[@johnstone_Recognition_1997], or to provide erroneous information [@johnstone_Badges_1993]. 
Typically, in a given context, some proportion of individuals will benefit 
from broadcasting accurate information, whereas others will benefit from hiding it. 
Take, for instance, an interaction between two individuals where one can help the other. 
Given some costs and benefits, a potential donor will be interested in helping 
related individuals. Therefore, for a relative of the donor, 
broadcasting kinship is advantageous, whereas for an unrelated individual, 
concealing the lack of kinship is better. Similar scenarios may apply to 
many aspects of social life such as finding mates, feeding offspring, dominance relationships 
and aggressive interactions [@bradbury_Principles_2011; @moller_Female_1988; @tibbetts_Socially_2004].
In dominance and aggressive interactions, an important piece of
information to guide individual actions is interacting partners fighting ability, 
which is sometimes referred to as Resource Holding Potential (RHP) [@parker_Assessment_1974], 
or simply as quality. Responsiveness to the quality of the 
partner is central to communication systems such as badges of status, 
where an arbitrary signal conveys quality [@johnstone_Badges_1993; @rohwer_Social_1975a]. 
Here, arbitrary refers to a signal which is not ontogenetically correlated with quality. 
Badges of status can be evolutionarily stable whenever the signal imposes a fitness cost which 
decreases with the quality of an individual  [@botero_Evolution_2010; @johnstone_Badges_1993], 
such that it's no longer in the interest of low quality individuals to fake quality by producing a
large badge. The cost of honest signals is a more general principle of communications systems, 
usually referred to as the handicap principle [@grafen_Biological_1990; @zahavi_Mate_1975]. 
An alternative system of communication is one where individuals gather and store information
about each individual they interact with. This information should reliably allow 
each individual to react adaptively to the quality difference with their opponent. 
This type of assessment strategy is often referred to as individual recognition [@whitfield_Plumage_1986]. Evidently, individual recognition is restricted to 
certain interaction structures, because individuals are limited by cognitive 
abilities in how many individuals they can recognize and track. Thus, individual 
recognition and badges of status have been assumed to be alternative communication 
systems fulfilling the same function, reducing the costs of aggression in contests over resources. 
Furthermore, badges of status and individual recognition are expected to evolve under different interaction structures, badges of status under global interactions and individual recognition
under local interactions [@dale_Signaling_2001; @sheehan_There_2016].  There is no clear cut reason, however, why both systems could not work together, in fact there is some evidence
that they can [@chaine_Manipulating_2018].

@@

Associative learning is a key cognitive mechanism that allows individuals to associate
rewards with environmental stimuli and thus behave adaptively [@staddon_Adaptive_2016]. 
Associative learning exists in all major vertebrate taxa, and in many invertebrates [@heyes_Simple_2012;@macphail_Brain_1982; @staddon_Adaptive_2016; @behrens_Associative_2008].
Theory has shown that natural selection favors these associations in complex environments
where conditions are hard to predict [@dridi_Environmental_2016]. Besides its wide taxonomic and
ecological relevance, associative learning is a flexible cognitive mechanism whose underpinnings
show interspecific variation [@enquist_Power_2016; @quinones_Reinforcement_2019], so 
presumably, it has been modified by natural selection. Despite all this, associative 
learning is not often included in the narrative of evolutionary explanations of 
behavioural patterns [@fawcett_Exposing_2013; @kamil_Optimal_1983; @mcauliffe_Psychology_2015]. 
Computational models of evolution can play an important role to overcome the 
lack of integration between learning and evolution. Reinforcement learning theory 
encompases a series of computational methods inspired on the psychological and 
neurological mechanisms of associative learning [@sutton_Reinforcement_2018].
These set of algorithms allow the implementation of biologically realistic problems, 
capturing the essence of learning processes [@frankenhuis_Enriching_2018; @quinones_Reinforcement_2019]. 
Furthermore, these algorithms can be embedded in evolutionary simulations to 
generate theoretical predictions of the effect that learning can have in behavioral
evolution [@leimar_Learning_2019].

@@

We model the evolution of signals of quality in the context of agonistic interactions by 
modelling a population of haploid individuals with non-overlaping generations. 
Individuals are born every generation with a level of quality ($Q_i$, where $i$ is subscript 
of the population vector of size $N$) given by a number between zero and one, which is drawn 
from a truncated normal distribution $N(\mu = 0.5,\sigma)$. 
An individual with quality $0$ has the lowest RHP, 
while an individual with quality $1$ has the highest. As part of development processes
individuals produce a morphological signal (badge), the size of such depends on their level 
of quality according to a reaction norm given by $B_i=1/(1+e^{\alpha_i-\beta_i Q_i})$;
where are $\alpha_i$ and $\beta_i$ are individual specific traits that determine 
the shape of the reaction norm (Fig. \ref{fig:model-struc} A). Variation in $\alpha_i$ and $\beta_i$ means individuals can have either uninformative (flat) or informative (logistic) norms. 
The size of the signal is constrained between zero and one. We assume different values of these traits 
are given by different alleles, and are inherited from mother to offspring. 
Unless, with a small probability, mutation changes the allelic value of the offspring.
After birth individuals go through a round of viability selection. 
Individual specific survival probability is given by $s_i=1/(1+e^{-k_1-k_2(Q_i-B_i)})$. 
Where $k_1$ and $k_2$ are parameter values determining the shape of the survival function. 
Importantly, if $k_2=0$ survival probability is independent of quality, while if $k_2>0$
lower quality individuals pay a higher price for s similar-sized badge, fulfilling the core assumption 
of the handicap principle [@botero_Evolution_2010; @grafen_Biological_1990; @johnstone_Badges_1993].

@@

rangx<-seq(0,1,by=0.01)
  dataIndsAct<-sapply(as.list(tempPop[nInteract==behavTime,indId]),
                      function(x){x=
                        logist(totRBF(rangx,
                                      centers,sigSquar,
                                      as.double(
                                        tempPop[(nInteract==behavTime
                                                 &indId==x)
                                                # &(Quality>0.8&Quality<1)
                                                ,.SD,
                                                .SDcol=grep("WeightAct",
                                                            names(tempPop),
                                                            value = TRUE)
                                                ])),alpha = 0,beta = 1)})
  # par(plt=posPlot(numploty = 4,numplotx = 4,idploty = 2,idplotx = 1))
  par(plt=posPlot(numploty = 1,numplotx = 2,idploty = 1,idplotx = 1,upboundx = 91))
matplot(x=rangx,y=dataIndsAct,type='l',xlab="",ylab="prob. retreat",
          xaxt="s",yaxt="s",lty = 1,
          col=paletteMeans(100)[
            findInterval(tempPop[nInteract==1700,Quality],colorbreaksQual)],
          lwd=0.5,ylim=c(0,1.1))
text(x = 0.08,y=1.05,"C",cex = 1.5)
par(new=FALSE)
color.bar.aeqp(paletteMeans1(100),min =min(colorbreaksQual),
               max = max(colorbreaksQual),nticks = 3,
               cex.tit = 0.9,title = "quality",
               numplotx = 20,numploty = 13,idplotx =9,idploty = 2)

@@

We first present the outcome of simulations where we prevent the evolution of the 
sender code (by setting the mutation rate to $0$), and assume that all individuals 
in the population display either an uninformative or informative badge size with respect to their quality. These simulations show what type of receiver strategy develops through a learning process. 
Figure \ref{fig:model-struc} (C and D) shows the receiver strategy developed 
through learning; panel C is for receivers that faced uninformative signals, 
and D informative ones. When learners face uninformative signals, they change their 
probability of retreating depending on their own quality. Individuals with higher 
quality (red tones), after the learning process, have a high probability of attacking; while 
individuals of lower quality (blue tones) mostly retreat from confrontations. Thus, learning splits
the population of receivers into the two classic pure strategies of hawks and doves. 
Given that we have a assumed a monomorphic population with unresponsive reaction norms 
on the signalling side, the changes triggered by learning only affect a small range 
of badge sizes. In contrast, when receivers face informative reaction norms 
on the side of the signaller (panel B in fig. \ref{fig:model-struc}), receivers use the 
badge size of their interacting partners to determine whether to retreat or attack. 
The relationship is given by a threashold-like reaction norm, where the change from 
retreating to attacking depends on the quality of the receiver. As expected, 
the higher the quality of the receiver the larger the badge size that triggers a retreat.

When we allow the evolution of the sender code ($\alpha$ and $\beta$ change subject to natural selection and genetic drift), and the badge size works as a handicap 
(i.e. the cost of the badge is inversely proportional to the quality of the individual), the sender code evolves to produce an honest signalFig \ref{fig:handicap}).

>>>>

---
title: |
  | Learning can mediate both badges of status and individual recognition
author:
- Andrés E. Quiñones^[Laboratorio de Biología Evolutiva de Vertebrados, Departamento
  de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia]
- C. Daniel Cadena*
- Olof Leimar^[Department of Zoology, Stockholm University, Stockholm, Sweden]
- Redouan Bshary^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  word_document: default
fig_caption: yes
fontsize: 12pt
header-includes:
- \usepackage{float}
- \usepackage{setspace}\doublespacing
- \linespread{2}
- \usepackage{lineno}
- \linenumbers
- \floatplacement{figure}{H}
keep_tex: yes
keywords: My keywords
linespread: 2
bibliography: ../SocialMorphCue.bib
spacing: double
style: C:\Users\andre\Zotero\styles\elife.csl
abstract: Adaptive behavioural responses often depend on qualities of the interacting partner of an individual. For example, when competing for resources, an individual might be better off escalating fights with individuals of lower quality, while restraining from fighting individuals of higher quality. Communication systems involving signals of quality allow individuals to reduce uncertainty regarding the fighting ability of their partners and make more adaptive behavioral decisions. However, dishonest individuals can destabilize such communications systems. One open question is whether cognitive mechanisms, such as learning, can maintain the honesty of signals, thus, favoring their evolutionary stability. Here we present evolutionary simulations, where individuals can produce a signal proportional to their quality; and learn along their lifetime the best response to the signal emitted by their peers. In these simulations, learning on the receiver side can mediate the evolution of signals of quality on the sender side. When the cost of the signal is proportional to the quality of the sender populations are only composed of honest signalers. When the cost is not proportional to the quality of the signaler, the population is composed of both honest and dishonest signalers. We argue that learning can be a general cognitive mechanism playing a role in a wide range of communication systems.  
---

@@

The outcome of interactions with con-specifics is an important 
determinant of fitness in social animals. Irrespective of whether such interactions are cooperative 
or competitive, the actions of interacting individuals partly determine 
their reproductive success. However, the best action for an individual 
might vary depending on its condition, and that of individuals with whom it interacts. 
Thus, acting based on information about interacting 
partners is typically adaptive [@quinones_Negotiation_2016].
Acquiring this information, however, is far from trivial. 
In some cases, interacting partners (signallers) might be 'willing' to provide accurate
information, but in others it might be in their own interest to conceal information
[@johnstone_Recognition_1997], or to provide erroneous information [@johnstone_Badges_1993]. 
Typically, in a given context, some proportion of individuals will benefit 
from broadcasting accurate information, whereas others will benefit from hiding it. 
Take, for instance, an interaction between two individuals where one can help the other. 
Given some costs and benefits, a potential donor will be interested in helping 
related individuals. Therefore, for a relative of the donor, 
broadcasting kinship is advantageous, whereas for an unrelated individual, 
concealing the lack of kinship is better. Similar scenarios may apply to 
many aspects of social life such as finding mates, feeding offspring, dominance relationships 
and aggressive interactions [@bradbury_Principles_2011; @moller_Female_1988; @tibbetts_Socially_2004].
In dominance and aggressive interactions, an important piece of
information to guide individual actions is interacting partners fighting ability, 
which is sometimes referred to as Resource Holding Potential (RHP) [@parker_Assessment_1974], 
or simply as quality. Responsiveness to the quality of the 
partner is central to communication systems such as badges of status, 
where an arbitrary signal conveys quality [@johnstone_Badges_1993; @rohwer_Social_1975a]. 
Here, arbitrary refers to a signal which is not ontogenetically correlated with quality. 
Badges of status can be evolutionarily stable whenever the signal imposes a fitness cost which 
decreases with the quality of an individual  [@botero_Evolution_2010; @johnstone_Badges_1993], 
such that it's no longer in the interest of low quality individuals to fake quality by producing a
large badge. The cost of honest signals is a more general principle of communications systems, 
usually referred to as the handicap principle [@grafen_Biological_1990; @zahavi_Mate_1975]. 
An alternative system of communication is one where individuals gather and store information
about each individual they interact with. This information should reliably allow 
each individual to react adaptively to the quality difference with their opponent. 
This type of assessment strategy is often referred to as individual recognition [@whitfield_Plumage_1986]. Evidently, individual recognition is restricted to 
certain interaction structures, because individuals are limited by cognitive 
abilities in how many individuals they can recognize and track. Thus, individual 
recognition and badges of status have been assumed to be alternative communication 
systems fulfilling the same function, reducing the costs of aggression in contests over resources. 
Furthermore, badges of status and individual recognition are expected to evolve under different interaction structures, badges of status under global interactions and individual recognition
under local interactions [@dale_Signaling_2001; @sheehan_There_2016].  There is no clear cut reason, however, why both systems could not work together, in fact there is some evidence
that they can [@chaine_Manipulating_2018].

@@

Associative learning is a key cognitive mechanism that allows individuals to associate
rewards with environmental stimuli and thus behave adaptively [@staddon_Adaptive_2016]. 
Associative learning exists in all major vertebrate taxa, and in many invertebrates [@heyes_Simple_2012;@macphail_Brain_1982; @staddon_Adaptive_2016; @behrens_Associative_2008].
Theory has shown that natural selection favours these associations in complex environments
where conditions are hard to predict [@dridi_Environmental_2016]. Besides its wide taxonomic and
ecological relevance, associative learning is a flexible cognitive mechanism whose underpinnings
show interspecific variation [@enquist_Power_2016; @quinones_Reinforcement_2019], so 
presumably, it has been modified by natural selection. Despite all this, associative 
learning is not often included in the narrative of evolutionary explanations of 
behavioural patterns [@fawcett_Exposing_2013; @kamil_Optimal_1983; @mcauliffe_Psychology_2015]. 
Computational models of evolution can play an important role to overcome the 
lack of integration between learning and evolution. Reinforcement learning theory 
encompasses a series of computational methods inspired on the psychological and 
neurological mechanisms of associative learning [@sutton_Reinforcement_2018].
These set of algorithms allow the implementation of biologically realistic problems, 
capturing the essence of learning processes [@frankenhuis_Enriching_2018; @quinones_Reinforcement_2019]. 
Furthermore, these algorithms can be embedded in evolutionary simulations to 
generate theoretical predictions of the effect that learning can have in behavioural
evolution [@leimar_Learning_2019].

@@

We model the evolution of signals of quality in the context of agonistic interactions by 
modelling a population of haploid individuals with non-overlapping generations. 
Individuals are born every generation with a level of quality ($Q_i$, where $i$ is subscript 
of the population vector of size $N$) given by a number between zero and one, which is drawn 
from a truncated normal distribution $N(\mu = 0.5,\sigma)$. 
An individual with quality $0$ has the lowest RHP, 
while an individual with quality $1$ has the highest. As part of development processes
individuals produce a morphological signal (badge), the size of such depends on their level 
of quality according to a reaction norm given by $B_i=1/(1+e^{\alpha_i-\beta_i Q_i})$;
where are $\alpha_i$ and $\beta_i$ are individual specific traits that determine 
the shape of the reaction norm (Fig. \ref{fig:model-struc} A). Variation in $\alpha_i$ and $\beta_i$ means individuals can have either uninformative (flat) or informative (logistic) norms. 
The size of the signal is constrained between zero and one. We assume different values of these traits 
are given by different alleles, and are inherited from mother to offspring. 
Unless, with a small probability, mutation changes the allelic value of the offspring.
After birth individuals go through a round of viability selection. 
Individual specific survival probability is given by $s_i=1/(1+e^{-k_1-k_2(Q_i-B_i)})$. 
Where $k_1$ and $k_2$ are parameter values determining the shape of the survival function. 
Importantly, if $k_2=0$ survival probability is independent of quality, while if $k_2>0$
lower quality individuals pay a higher price for s similar-sized badge, fulfilling the core assumption 
of the handicap principle [@botero_Evolution_2010; @grafen_Biological_1990; @johnstone_Badges_1993].

@@

rangx<-seq(0,1,by=0.01)
  dataIndsAct<-sapply(as.list(tempPop[nInteract==behavTime,indId]),
                      function(x){x=
                        logist(totRBF(rangx,
                                      centers,sigSquar,
                                      as.double(
                                        tempPop[(nInteract==behavTime
                                                 &indId==x)
                                                # &(Quality>0.8&Quality<1)
                                                ,.SD,
                                                .SDcol=grep("WeightAct",
                                                            names(tempPop),
                                                            value = TRUE)
                                                ])),alpha = 0,beta = 1)})
  # par(plt=posPlot(numploty = 4,numplotx = 4,idploty = 2,idplotx = 1))
  par(plt=posPlot(numploty = 1,numplotx = 2,idploty = 1,idplotx = 1,upboundx = 91))
matplot(x=rangx,y=dataIndsAct,type='l',xlab="",ylab="prob. retreat",
          xaxt="s",yaxt="s",lty = 1,
          col=paletteMeans(100)[
            findInterval(tempPop[nInteract==1700,Quality],colorbreaksQual)],
          lwd=0.5,ylim=c(0,1.1))
text(x = 0.08,y=1.05,"C",cex = 1.5)
par(new=FALSE)
color.bar.aeqp(paletteMeans(100),min =min(colorbreaksQual),
               max = max(colorbreaksQual),nticks = 3,
               cex.tit = 0.9,title = "quality",
               numplotx = 20,numploty = 10,idplotx =9,idploty = 2)

@@

We first present the outcome of simulations where we prevent the evolution of the 
sender code (by setting the mutation rate to $0$), and assume that all individuals 
in the population display either an uninformative or informative badge size with respect to their quality. These simulations show what type of receiver strategy develops through a learning process. 
Figure \ref{fig:model-struc} (C and D) shows the receiver strategy developed 
through learning; panel C is for receivers that faced uninformative signals, 
and D informative ones. When learners face uninformative signals, they change their 
probability of retreating depending on their own quality. Individuals with higher 
quality (red tones), after the learning process, have a high probability of attacking; while 
individuals of lower quality (blue tones) mostly retreat from confrontations. Thus, learning splits
the population of receivers into the two classic pure strategies of hawks and doves. 
Given that we have a assumed a monomorphic population with unresponsive reaction norms 
on the signalling side, the changes triggered by learning only affect a small range 
of badge sizes. In contrast, when receivers face informative reaction norms 
on the side of the signaller (panel B in fig. \ref{fig:model-struc}), receivers use the 
badge size of their interacting partners to determine whether to retreat or attack. 
The relationship is given by a threshold-like reaction norm, where the change from 
retreating to attacking depends on the quality of the receiver. As expected, 
the higher the quality of the receiver the larger the badge size that triggers a retreat.

```{r handicap,echo=FALSE,out.width='90%',fig.align='center',fig.show='hold',fig.cap="Evolution of the badge size as a handicap mediated by learning. Middle panels show the evolutionary dynamics of the sender code. On the left, changes in the distribution of values for the intercept of the reaction norm ($\\alpha$); on the right changes in the distribution of the slope ($\\beta$). Dashed lines in both panels show the mean of the distribution. Grey lines show the generation time corresponding to the panels above and below showing the sender and receiver code. In the panels above, the reaction norms correspond to individuals in the population after the interaction round. Color scale indicates quality just as in Fig. \\ref{fig:model-struc}. In the panels below, colors represent a cluster clasification performed by the k-means algorithm" }

knitr::include_graphics(here("Simulations","betCostEvol1_","evolDyn0_betCost5.png"))

When we allow the evolution of the sender code ($\alpha$ and $\beta$ change subject to natural selection and genetic drift), and the badge size work as a handicap 
(i.e. the cost of the badge is inversely proportional to the quality of the individual), the sender code evolves to produce an honest signal Fig \ref{fig:handicap}). The evolution of 
the sender code does not happen immediately after the start of the evolutionary process. Instead, the evolutionary dynamics of the  reaction norm parameters (Fig. \ref{fig:handicap}, X) show a set of 
steps. First, the intercept of the reaction norm ($\alpha$) evolves to higher values, reducing the 
average badge size in the populations. That makes sense because reaction norms segregating in the population are flat at this point, and consequently the receiver code does not respond to the badge size, bigger badges are costlier and do not trigger lower attack probabilities. During those first generations, the slope of the sender reaction norm ($\beta$)  remains around the initial value of zero. At around generation 4000, the slope evolves toward positive values. Which implies that larger badges correlate with higher quality. Receivers learn to react to such correlation, reducing 
the probability of attack towards individual of larger badges. Hence, natural selection 
favours larger values of $\beta$, eventually leading to an evolutionary equilibrium where 
badge size is an honest signal of quality mediated by the learned responses of receivers. The
evolutionary trajectory portrayed in figure \ref{fig:handicap} is not the only possible trajectory. 
If the slope of the sender reaction norms ($\beta$) evolves toward negative values before badges become handicaps, receivers never learn to react to the size of badges. Thus, badges are only costly and do not provide information about the quality of an individual. Eventually, the badge disappears from the population.

When production of the badge is not costly (i.e. does not work as a handicap), the parameters of the sender code go through evolutionary branching event, triggereing the evolution of different types of
signals in the population. Fig. \ref{fig:branching}A and B shows changes in the distribution of the 
sender reaction norm ($\alpha$ and $\beta$) along evolutionary time. Darker areas show trait values 
with high frequency in the population. Populations start monomorphic with a value of zero on both traits, and mutations quickly buid up a normal distribution around the starting value. Within the first 2000 generations the unimodal distribution splits into a bimodal one. In the case of $\alpha$, one of the peaks splits further, so at the end of the evolutionary simulation the distribution of $\alpha$ value in the population shows three peaks. In the case of $\beta$, the two initial peaks coexist for around 4000 generations. Later on one of the types goes extinct and the distribution goes back to being unimodal. These changes in the distrubtuion of the sender reaction norm parameters imply that during the second half of the simualation individuals can by classify into three distinct types. Two types express a flat reaction norm, meaning that their badge size is not informative of their quality, while the third type shows intermediate badge sizes which are determined by the quality of the individual (Fig. \ref{fig:branching}). Furthermore, the receiver reaction norms develop through learning, particularly those of individuals of intermediate quality, respond to the signal of their sender type by increasing the probability of retreating from a fight with individuals with larger badges (Fig. \ref{fig:branching}).

```{r branching,echo=FALSE,out.width='90%',fig.align='center',fig.show='hold',fig.cap= "The evolution of cheap signals. Portrait of the evolutionary dynamics of the sender code with snapsots of both sender and receiver codes just as in fig. \\ref{fig:handicap}. The middle panels show changes in the distribution of values fir $\\alpha$ and $\\beta$ along evolutionary time. Panels above and bellow correspond to snapshots of the sender and receiver codes, respectively, generation time of the snapshots are indicated by the grey lines in the middle panels."}

knitr::include_graphics(here("Simulations","nIntGroupNormQual_","evolDyn7_nIntGroup2000.png"))

```{r startCond, echo=FALSE, out.width='90%',fig.align='center',fig.show='hold',fig.cap="WHy would you want to be recognized"}

knitr::include_graphics("../Simulations/initAct_/indVarScatter_.png")
